---
title: "Protective Behaviors Paper"
author: "Kim Johnson"
date: '2022-07-01'
output: html_document
---
# Load package and libraries 
```{r}
pacman::p_load(readxl, openxlsx, table1, dplyr, ggplot2, Hmisc, vtable, tidyr, ggrepel, patchwork, segmented, lubridate, miceadds, lme4, readr, geepack, gee, odds.n.ends, patchwork, lubridate, forestplot, lmtest, multcomp)
```

# Import combined survey file 
```{r}
Merged_survey <- read.xlsx("SurveyExport_Merged.xlsx")

Merged_survey$surveydate<-as.Date(Merged_survey$surveydate,origin="1899-12-30", format = "%Y-%m-%d")
colnames(Merged_survey)
# Filtering for survey dates between 10/17/2021 and  7/1/2022
Merged_survey <- Merged_survey %>%
  filter(surveydate < "2022-07-01" & surveydate >= "2021-10-17") %>%
  dplyr::select(ExternalReference, surveydate, PreventionFreq, COVIDStatus, CovidGet_1, COVIDSerious_1,gender_bl, age_cat, race_bl)

Baseline<-read_excel("Baseline.xlsx") # for Table 1

# limiting Baseline ids to those in merged survey
ids<-unique(Merged_survey$ExternalReference)

Baseline<-Baseline %>%
  filter(ExternalReference %in% ids)
```

#Getting STL City and County COVID-19 cases and hospitalizations (from the MO Hospital Organization)
```{r}
COVID_MOcases1<-read_delim("County Data.csv")
COVID_MOhosp1<-read_delim("Teletracking.csv")
COVID_MOcases2<-read_delim("County(through June 22).csv")
COVID_MOhosp2<-read_delim("Hospital(through June 22).csv")

# Limit case counts to St. Louis City and County
COVID_STcases1<-COVID_MOcases1 %>%
  filter(County_Desc %in% c("SAINT LOUIS", "SAINT LOUIS CITY")) %>%
  group_by(week_begining) %>%
  summarise(sum=sum(pcr_cases)) 

COVID_STcases2<-COVID_MOcases2 %>%
  filter(County_Desc %in% c("SAINT LOUIS", "SAINT LOUIS CITY")) %>%
  filter(week_begining %in% c("5/29/2022", "6/5/2022", "6/12/2022", "6/19/2022", "6/26/2022")) %>%
  group_by(week_begining) %>%
  summarise(sum=sum(pcr_cases))

# Bind case counts together
COVID_STcases<-rbind(COVID_STcases1, COVID_STcases2)

# Limit hospitalizations to St. Louis Region
COVID_SThosp1<-COVID_MOhosp1%>%
  filter(region=="Saint Louis Region") %>%
  rename(week_begining=dt)

COVID_SThosp2<-COVID_MOhosp2%>%
  filter(region=="Saint Louis Region")%>%
  filter(dt %in% c("5/29/2022", "6/5/2022", "6/12/2022", "6/19/2022", "6/26/2022")) %>%
  rename(week_begining=dt) 

# Bind hospitalization counts together
COVID_SThosp<-rbind(COVID_SThosp1, COVID_SThosp2)
```

# Get participants by week
```{r}
partbywk<-Merged_survey %>%
  group_by(surveydate) %>%
  summarise(n=n())
```

# Table 1：Descriptive analysis of demographics
```{r}
# Some data management
Baseline$age_cat<-factor(Baseline$age_cat, levels = c("18-29", "30-39", "40-49", "50-59", ">60"))
Baseline$gender_bl<-factor(Baseline$gender_bl, levels = c("Male", "Female", "Non-binary / third gender", "Prefer not to say"))
Baseline$hispanic_bl<-factor(Baseline$hispanic_bl, levels = c("Yes", "No", "Prefer not to say"))

Baseline$race_bl<-
  ifelse(Baseline$race_bl == "White", Baseline$race_bl,
    ifelse(Baseline$race_bl == "Black or African American", Baseline$race_bl,
      ifelse(Baseline$race_bl == "Asian or Asian American", Baseline$race_bl,
        ifelse(Baseline$race_bl == "Prefer not to say", Baseline$race_bl,
          ifelse(Baseline$race_bl == "Other (please specify)", "Other", "Two or more races")))))
Baseline$race_bl<-factor(Baseline$race_bl, levels = c("White", "Black or African American", "Asian or Asian American", "Two or more races", "Other", "Prefer not to say"))

Baseline$under12_bl<-factor(Baseline$under12_bl, levels = c("Yes", "No"))
Baseline$vax_received_bl<-factor(Baseline$vax_received_bl, levels = c("Yes, both doses of a 2-dose vaccine", "Yes, first dose of a 2-dose vaccine", "Yes, a 1-dose vaccine", "No, but I plan to get a COVID-19 vaccine", "No, and I don't plan to get a COVID-19 vaccine", "Prefer not to answer"))

# apply labels for table 1
label(Baseline$gender_bl)<-"Gender"
label(Baseline$race_bl)<-"Race"
label(Baseline$hispanic_bl)<-"Hispanic Ethnicity"
label(Baseline$partype)<-"Participant Type"
label(Baseline$vax_received_bl)<-"Vaccination Status"
label(Baseline$age_cat)<-"Age Category (years)"

table1(~gender_bl  + race_bl + hispanic_bl + age_cat + vax_received_bl, Baseline)

# calculate mean baseline worry for Blacks and Whites
mw<-Baseline %>%
  group_by(race_bl) %>%
  dplyr::summarize(mean=mean(worry_bl_1, na.rm=TRUE), sd=sd(worry_bl_1, na.rm=TRUE))
```

# Line plots for protection behaviors
```{r}
# get percentages of protection behaviors
PF<-Merged_survey %>%
  group_by(surveydate, PreventionFreq) %>%
  filter(!is.na(PreventionFreq)) %>%
  summarise(Percentage=n()) %>% 
  mutate(Percentage=Percentage/sum(Percentage)*100) 

PF$PreventionFreq <- factor(PF$PreventionFreq, levels=c("About the same as you did one week ago?", "Less than you did one week ago?", "More than you did one week ago?"), labels=c("Same", "Less", "More Prevention Behaviors"))
table(PF$PreventionFreq)

PF2<-PF %>% 
  filter(PreventionFreq =="More Prevention Behaviors") %>%
  ggplot(aes(x=surveydate, y=Percentage, color=PreventionFreq)) +
  geom_point()+
  geom_line(aes(linetype=PreventionFreq))+
  ylim(0,100)+
  theme_classic() +
  ggtitle("PreventionFreq", "To prevent the spread of COVID-19, \n some people wear masks, \n wash their hands often, avoid close contact with others, \n and avoid large indoor gathers. \n Are you doing these things:") +
  theme(plot.title = element_text(color = "black", size = 12, face = "bold"),
  plot.subtitle = element_text(size=8, color = "black"), legend.text = element_text(size=8, face="bold")) +
  guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
    scale_x_date(date_labels="%m/%d/%y", breaks = PF$surveydate) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
PF2
```

# Data management for plotting covid status
```{r}
CovidStat<-Merged_survey %>%
  mutate(CS_infection=if_else(grepl('household_closecontact',COVIDStatus)|
                              grepl('household_test', COVIDStatus)|
                              grepl('household_closecontact',COVIDStatus)|
                              grepl('household_test',COVIDStatus)|
                              grepl('household_sick', COVIDStatus)|
                              grepl('household_hospital', COVIDStatus)|
                              grepl('household_sick', COVIDStatus)|grepl('household_hospital',COVIDStatus), 1, 0)) %>%
  mutate(CS_none=if_else(grepl('household_none', COVIDStatus)|grepl('household_none', COVIDStatus), 1, 0))

CovidStat$CS_infection <- factor(CovidStat$CS_infection, levels=c(1:0), labels=c("Self or close contact COVID infected", "No one COVID infected"))
CovidStat$CS_none <- factor(CovidStat$CS_none, levels=c(1:0), labels=c("None", "Not none"))

table(CovidStat$CS_infection)
table(CovidStat$CS_infection)
table(CovidStat$CS_none)
```

# Covid infection in last week
```{r}
#CS_infected
CovidStat2<-CovidStat %>%
  group_by(surveydate, CS_infection) %>%
  summarise(Percentage=n()) %>% 
  mutate(Percentage=Percentage/sum(Percentage)*100) 

CovidStat3<-CovidStat2 %>% 
  ggplot(aes(x=surveydate, y=Percentage, color=CS_infection)) +
  geom_point()+
  geom_line()+
  ylim(0,100)+
  theme_classic() +
  ggtitle("CS_infection", "In the last week, have you or a household member… (choose all)") +
  theme(plot.title = element_text(color = "black", size = 12, face = "bold"),
  plot.subtitle = element_text(size=8, color = "black"), legend.text = element_text(size=8, 
                                     face="bold")) +
  guides(fill=guide_legend(nrow=2,byrow=TRUE)) +
    scale_x_date(date_labels="%m/%d/%y", breaks = PF$surveydate) +
    theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))
CovidStat3
```

# No one in household sick or hospitalized in last week
```{r}
# CS_none
CovidStat6<-CovidStat %>%
  group_by(surveydate, CS_none) %>%
  summarise(Percentage=n()) %>% 
  mutate(Percentage=Percentage/sum(Percentage)*100) 

CovidStat7<-CovidStat6 %>% 
  ggplot(aes(x=surveydate, y=Percentage, color=CS_none)) +
  geom_point()+
  geom_line()+
  ylim(0,100)+
  theme_classic() +
  ggtitle("CS_none", "In the last week, have you or a household member… (choose all)") +
  theme(plot.title = element_text(color = "black", size = 12, face = "bold"),
  plot.subtitle = element_text(size=8, color = "black"), legend.text = element_text(size=8, 
                                     face="bold")) +
  guides(fill=guide_legend(nrow=2,byrow=TRUE))
CovidStat7


pdf("Other variable plots2.pdf", width=15, height=10, paper="USr", onefile=FALSE)
CovidStat3 + CovidStat7 + plot_layout(ncol=1, nrow=3, guides='keep') &
  theme(legend.position='bottom')
dev.off()
```

# Create dataframe limiting to protective behaviors
```{r}
PF_limited<-PF %>%
  filter(PreventionFreq=="More Prevention Behaviors") 
PF_limited<-as.data.frame(PF_limited)
```

# Create dataframe limiting to infection
```{r}
CovidStat3

CovidStat3_limited<-CovidStat2 %>%
  filter(CS_infection=="Self or close contact COVID infected") 

CovidStat3_limited<-as.data.frame(CovidStat3_limited)
new_row5 <- data.frame("2021-10-10", "Self or close contact COVID infected", 0)
names(new_row5)<-c("surveydate","CS_infection","Percentage")
new_row6 <- data.frame("2022-02-27", "Self or close contact COVID infected", 0)
names(new_row6)<-c("surveydate","CS_infection","Percentage")
CovidStat3_limited <- rbind(CovidStat3_limited, new_row5, new_row6) %>% 
  arrange(surveydate)
```

# Align survey date with MO HOSP files week beginning dates (PF file is for graphing)
```{r}
fixdates<-function(data){
data<-data %>%
  mutate(week_begining=case_when(surveydate=="2021-08-30" ~"8/29/2021",
                                  surveydate=="2021-09-06" ~"9/5/2021",
                                  surveydate=="2021-09-07" ~"9/5/2021",
                                  surveydate=="2021-09-13" ~"9/12/2021",
                                  surveydate=="2021-09-15" ~"9/12/2021",
                                  surveydate=="2021-09-20" ~"9/19/2021",
                                  surveydate=="2021-09-21" ~"9/19/2021",
                                  surveydate=="2021-09-26" ~"9/26/2021",
                                  surveydate=="2021-10-03" ~"10/3/2021",
                                  surveydate=="2021-10-10" ~"10/10/2021",
                                  surveydate=="2021-10-17" ~"10/17/2021",
                                  surveydate=="2021-10-24" ~"10/24/2021",
                                  surveydate=="2021-10-31" ~"10/31/2021",
                                  surveydate=="2021-11-07" ~"11/7/2021",
                                  surveydate=="2021-11-14" ~"11/14/2021",
                                  surveydate=="2021-11-21" ~"11/21/2021",
                                  surveydate=="2021-11-28" ~"11/28/2021",
                                  surveydate=="2021-12-05" ~"12/5/2021",
                                  surveydate=="2021-12-12" ~"12/12/2021",
                                  surveydate=="2021-12-19" ~"12/19/2021",
                                  surveydate=="2021-12-26" ~"12/26/2021",
                                  surveydate=="2022-01-02" ~"1/2/2022",
                                  surveydate=="2022-01-09" ~"1/9/2022",
                                  surveydate=="2022-01-16" ~"1/16/2022",
                                  surveydate=="2022-01-23" ~"1/23/2022",
                                  surveydate=="2022-01-30" ~"1/30/2022",
                                  surveydate=="2022-02-06" ~"2/6/2022",
                                  surveydate=="2022-02-13" ~"2/13/2022",
                                  surveydate=="2022-02-20" ~"2/20/2022",
                                  surveydate=="2022-02-27" ~"2/27/2022",
                                  surveydate=="2022-03-06" ~"3/6/2022",
                                  surveydate=="2022-03-13" ~"3/13/2022",
                                  surveydate=="2022-03-20" ~"3/20/2022",
                                  surveydate=="2022-03-27" ~"3/27/2022",
                                  surveydate=="2022-04-03" ~"4/3/2022",
                                  surveydate=="2022-04-10" ~"4/10/2022",
                                  surveydate=="2022-04-17" ~"4/17/2022",
                                  surveydate=="2022-04-24" ~"4/24/2022",
                                  surveydate=="2022-05-01" ~"5/1/2022",
                                  surveydate=="2022-05-08" ~"5/8/2022",
                                  surveydate=="2022-05-15" ~"5/15/2022",
                                  surveydate=="2022-05-22" ~"5/22/2022",
                                  surveydate=="2022-05-29" ~"5/29/2022",
                                  surveydate=="2022-06-07" ~"6/5/2022",
                                  surveydate=="2022-06-13" ~"6/12/2022",
                                  surveydate=="2022-06-19" ~"6/19/2022",
                                  surveydate=="2022-06-26" ~"6/26/2022"
                                  ))
}
PF_limited<-fixdates(PF_limited)

CovidStat<-fixdates(CovidStat)
CovidStat3_limited<-fixdates(CovidStat3_limited)

# merge PF_limited with COVID_STcases to get St. Louis City and County cases in one dataset for graphing (through June 2022)
PF_limited<-left_join(PF_limited, COVID_STcases, by="week_begining")

# merge CovidStat with COVID_STcases that goes through June 2022
CovidStat<-left_join(CovidStat, COVID_STcases, by="week_begining")

# merge CovidStat3_limited (close contact infection) with COVID_STcases that goes through June 2022
CovidStat3_limited<-left_join(CovidStat3_limited, COVID_STcases,  by="week_begining")
```

#Prepare hospitalization dataset to add to 
```{r}
# format date
COVID_SThosp$week_begining<-as.Date(COVID_SThosp$week_begining, "%m/%d/%Y")

hosp<-COVID_SThosp %>%
  filter(week_begining>"2021-08-22") %>%
  dplyr::select(week_begining, total_covid_hospitalized)

# merge Merged_survey with hospitalizations that goes through 6/2022
CovidStat$week_begining<-as.Date(CovidStat$week_begining, "%m/%d/%Y")

CovidStat<-left_join(CovidStat, hosp, by="week_begining")

# select variables
colnames(CovidStat)

# create analytic dataset
MSV4models<-CovidStat %>%
  dplyr::select(ExternalReference, PreventionFreq, CS_infection, CS_none, surveydate, sum, total_covid_hospitalized, gender_bl, age_cat, week_begining, race_bl, CovidGet_1)

# this data is for other analyses below
Baseline2<-Baseline %>%
  dplyr::select(ExternalReference, think_bl_1, worry_bl_1) # think and worry are baseline variables

MSV4models<-left_join(Baseline2, MSV4models, by="ExternalReference") # join with Baseline variables to bring in think and worry
```


#Graphs for More Protective Behaviors in association with case counts, positive household contacts
```{r}
# Graph of COIVD_STL data with More Preventative Behaviors (updated with case counts May 2022 file=CovidStat4_limited)

# delete dates without case counts and create datasets to merge into one big dataset
PF_limited1<-PF_limited %>%
  filter(!is.na(sum)) %>%
  rename(STL_Cases=sum, Variable=PreventionFreq) # more protective behaviors than last week

CovidStat3_limited1<-CovidStat3_limited %>%
  filter(!is.na(sum)) %>%
  rename(STL_Cases=sum, Variable=CS_infection)  # infection last week

# cbind together

Data4Plot<-rbind(PF_limited1, CovidStat3_limited1)

# covert to date formats
Data4Plot$week_begining<-as.Date(Data4Plot$week_begining, "%m/%d/%Y")

# merge with hospitalizations
Data4Plot<-left_join(Data4Plot, hosp, by="week_begining")

# drop dates 10/17/2022 or earlier due to small numbers
Data4Plot<-Data4Plot %>%
  filter(surveydate>="2021-10-17")
```


# Figure 1
```{r}
p1<-Data4Plot %>%
  group_by(surveydate) %>%
  filter(Variable %in% c("More Prevention Behaviors", "Self or close contact COVID infected")) %>%
  
ggplot() + 
  geom_point(aes(surveydate, Percentage, color=Variable)) +
  geom_line(aes(surveydate, Percentage, color=Variable)) +
  geom_line(aes(week_begining, STL_Cases/200), colour="red") +
  geom_point(aes(week_begining, STL_Cases/200), colour="red") +
  scale_y_continuous(sec.axis=sec_axis(~.*200, name="St. Louis Region PCR positive cases")) +
  xlab("Date") + 
  scale_x_date(date_labels="%m/%d/%y", breaks=Data4Plot$surveydate, date_breaks="2 weeks")+ 
  scale_color_manual(values=c('blue','black')) +
  theme(axis.text.y.right=element_text(colour="red"),
        axis.title.y.right=element_text(colour="black"),
        axis.text.y=element_text(colour="black"),
        axis.title.y=element_text(colour="black"),
        axis.title.x=element_blank(),
        legend.position="bottom",
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, face="bold")) 
p1


pdf("Figure1.pdf", width=15, height=10, paper="USr")
p1  + plot_layout(ncol=1, nrow=1, guides='keep') &
  theme(legend.position='bottom')
dev.off()
```

# Dataset for logistic analyses that asks whether individuals reports more protective behaviors than the week before in when case counts are high or when they are sick or a close contact is sick
```{r}
# creating the MoreProtect and CloseContact variables
MSV4models <- MSV4models %>%
  mutate(MoreProtect = if_else(PreventionFreq == 'More than you did one week ago?', 1 , 0)) %>%
  mutate(CloseContact= if_else(CS_infection=="Self or close contact COVID infected", 1, 0)) 

#get quantiles based on survey days, need to limit dataset to unique dates
dates<-MSV4models %>%
  dplyr::select(surveydate, sum, total_covid_hospitalized)
dates<-unique(dates)

# get quantiles
quantile(dates$sum) 
quantile(dates$total_covid_hospitalized) 

MSV4models <- MSV4models%>% # make quartile categories for case counts
  mutate(CC_cat = if_else(sum< 1051, 0 ,
                          if_else(sum >=1051 & sum<2147, 1,
                                 if_else(sum >=2147 & sum<3306, 2,
                                        if_else(sum>=3306, 3, NULL)))))
MSV4models$CC_cat<-as.factor(MSV4models$CC_cat)
table(MSV4models$CC_cat)

MSV4models <- MSV4models%>% # make quartile categories for hospitalized counts
  mutate(TCV_cat = if_else(total_covid_hospitalized< 276.5, 0 , 
                           if_else(total_covid_hospitalized >=276.5 & total_covid_hospitalized< 479, 1,
                                        if_else(total_covid_hospitalized >=479 & total_covid_hospitalized<794, 2,
                                        if_else(total_covid_hospitalized>=794, 3, NULL)))))
MSV4models$TCV_cat<-as.factor(MSV4models$TCV_cat)
table(MSV4models$TCV_cat)

# plot MoreProtect by survey data according to CC_cat
p<-ggplot(MSV4models) +
  geom_point(aes(surveydate, MoreProtect,  color=CC_cat)) +
  facet_wrap(~ExternalReference)
p

# categorize covid worry and covid think variables at median
# Get median for dataset with unique external ref
unique<-MSV4models %>%
  dplyr::select(ExternalReference, think_bl_1, worry_bl_1)

summary(unique$worry_bl_1)
summary(unique$think_bl_1)
summary(as.numeric(MSV4models$CovidGet_1))

# convert CovidGet_1 to numeric
MSV4models$CovidGet_1<-as.numeric(MSV4models$CovidGet_1)

MSV4models<-MSV4models %>%
  mutate(worry_cat_bl=case_when(worry_bl_1>=45~1,
                              worry_bl_1<45~0),
         think_cat_bl=case_when(think_bl_1>=60 ~1,
                              think_bl_1<60 ~0)) %>%
  group_by(surveydate) %>%
  mutate(worry_cat_weekly=case_when(CovidGet_1 >=median(CovidGet_1)~1,
                                    CovidGet_1 < median(CovidGet_1)~0))


# factor worry and think
MSV4models$worry_cat_bl<-factor(MSV4models$worry_cat_bl, levels=c(0,1), labels=c("Worry < median", "Worry >= median"))
MSV4models$think_cat_bl<-factor(MSV4models$think_cat_bl, levels=c(0,1), labels=c("Think < median", "Think >= median")) 
MSV4models$worry_cat_weekly<-factor(MSV4models$worry_cat_weekly, levels=c(0,1), labels=c("Worry < median", "Worry >= median"))  
table(MSV4models$worry_cat_bl)
table(MSV4models$think_cat_bl)
table(MSV4models$worry_cat_weekly)

```


# Table 2: Mixed logistic models
```{r}
# Is case count category associated with more protective behavior than the week before?
glmer_glmCC<- glmer(data= MSV4models, MoreProtect ~ CC_cat + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC)

cc2<-confint.merMod(glmer_glmCC, method="Wald")
cc2<-as.data.frame(cc2[-c(1),])
ctab2 <- exp(cbind(est=fixef(glmer_glmCC),cc2))

# Is having a close contact or self infected associated with more protective behavior than the week before?
glmer_glm3a<- glmer(data= MSV4models, MoreProtect ~   CloseContact + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glm3a)

cc3a<-confint.merMod(glmer_glm3a, method="Wald")
cc3a<-as.data.frame(cc3a[-c(1),])
ctab3a<- exp(cbind(est=fixef(glmer_glm3a),cc3a))

# Case count adjusted for CloseContact 
glmer_glm5<- glmer(data= MSV4models, MoreProtect ~  CC_cat + CloseContact + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glm5)

cc5<-confint.merMod(glmer_glm5, method="Wald")
cc5<-as.data.frame(cc5[-c(1),])
ctab5<- exp(cbind(est=fixef(glmer_glm5),cc5))

# Weekly worry about Covid19 (ran because curious about this association)
glmer_glm6<- glmer(data= MSV4models, MoreProtect ~  worry_cat_weekly + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glm6)

cc6<-confint.merMod(glmer_glm6, method="Wald")
cc6<-as.data.frame(cc6[-c(1),])
ctab6<- exp(cbind(est=fixef(glmer_glm6),cc6))
```

# Effect modification (analyses only limited to males and females)
```{r}
# limit to males and females
MSV4models_gen<-MSV4models %>%
  filter(gender_bl %in% c("Female", "Male"))

# run gender model without interaction term
glmer_glmCC_genb<- glmer(data= MSV4models_gen, MoreProtect ~ CC_cat + CloseContact + gender_bl + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_genb)

# run gender model with interaction term
glmer_glmCC_gen<- glmer(data= MSV4models_gen, MoreProtect ~ CC_cat + CloseContact +  gender_bl + gender_bl*CC_cat + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_gen)

# get significance of interaction term
lrtest(glmer_glmCC_gen, glmer_glmCC_genb)

# Gender is not significant
```

# Effect modification (analyses only limited to whites and Black or African American)
```{r}
MSV4models_race<-MSV4models %>%
  filter(race_bl %in% c("White", "Black or African American")) %>%
  mutate(race_bl2=case_when(race_bl==c("White") ~0,
                            race_bl==c("Black or African American")~1)) # reverse reference

# run model without interaction term
glmer_glmCC_raceb<- glmer(data= MSV4models_race, MoreProtect ~ CC_cat+ race_bl +CloseContact +  (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_raceb)

# run model with interaction term
glmer_glmCC_race<- glmer(data= MSV4models_race, MoreProtect ~ CC_cat + race_bl + CloseContact + race_bl*CC_cat + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_race)

# get significance of interaction term
lrtest(glmer_glmCC_race, glmer_glmCC_raceb)

# Interaction is significant
```

# Table 2: Stratified estimates by race
```{r}
# Whites
MSV4models_white<-MSV4models %>%
  filter(race_bl %in% c("White"))

glmer_glmCC_white<- glmer(data= MSV4models_white, MoreProtect ~ CC_cat + CloseContact  + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_white)

cc6<-confint.merMod(glmer_glmCC_white, method="Wald")
cc6<-as.data.frame(cc6[-c(1),])
ctab6<- exp(cbind(est=fixef(glmer_glmCC_white),cc6))

MSV4models_black<-MSV4models %>%
  filter(race_bl %in% c("Black or African American"))

glmer_glmCC_black<- glmer(data= MSV4models_black, MoreProtect ~ CC_cat  + CloseContact + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_black)

cc7<-confint.merMod(glmer_glmCC_black, method="Wald")
cc7<-as.data.frame(cc7[-c(1),])
ctab7<- exp(cbind(est=fixef(glmer_glmCC_black),cc7))
```

# Effect modification (age)
```{r}
# collapse age categories
MSV4models_age <- MSV4models %>%
  mutate(age_cat2=case_when(age_cat %in% c("18-29", "30-39")~0,
         age_cat %in% c("40-49", "50-59") ~1,
         age_cat %in% c(">60") ~2))

# case count category
glmer_glmCC_age<- glmer(data= MSV4models_age, MoreProtect ~ CC_cat + age_cat2 + CloseContact + age_cat2*CC_cat + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_age)

# run age model
glmer_glmCC_ageb<- glmer(data= MSV4models_age, MoreProtect ~ CC_cat + age_cat2 + CloseContact + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_ageb)

# get significance of interaction term
lrtest(glmer_glmCC_age, glmer_glmCC_ageb)
```

# Close contact interactions
```{r}
# gender
glmer_glmCC_gen1<- glmer(data= MSV4models_gen, MoreProtect ~ CC_cat + CloseContact + gender_bl  + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_gen1)

glmer_glmCC_gen<- glmer(data= MSV4models_gen, MoreProtect ~ CC_cat + CloseContact + gender_bl +gender_bl*CloseContact + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_gen)

lrtest(glmer_glmCC_gen1, glmer_glmCC_gen)

# age
glmer_glmCC_age1<- glmer(data= MSV4models_age, MoreProtect ~ CC_cat + CloseContact + age_cat2  + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_age1)

glmer_glmCC_age<- glmer(data= MSV4models_age, MoreProtect ~ CC_cat +CloseContact + age_cat2 + age_cat2*CloseContact + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_age)

lrtest(glmer_glmCC_age1, glmer_glmCC_age)

# race 
glmer_glmCC_race1<- glmer(data= MSV4models_race, MoreProtect ~ CC_cat + CloseContact + race_bl2  + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_race1)

glmer_glmCC_race2<- glmer(data= MSV4models_race, MoreProtect ~  CC_cat + CloseContact + race_bl2 +race_bl2*CloseContact + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_race2)

# get significance of interaction term

lrtest(glmer_glmCC_race1, glmer_glmCC_race2)

```

# Interactions with weekly worry 
```{r}
#run worry model
glmer_glmCC_worryb<- glmer(data= MSV4models, MoreProtect ~ CC_cat + worry_cat_weekly + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_worryb)

#case count category
glmer_glmCC_worry<- glmer(data= MSV4models, MoreProtect ~ CC_cat + worry_cat_weekly + worry_cat_weekly*CC_cat + (1|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_worry)

lrtest(glmer_glmCC_worry, glmer_glmCC_worryb)

# no significant effect modification

# Difference by baseline in worry between blacks and whites
worry<-Baseline%>%
  filter(race_bl=="White")

summary(worry$worry_bl_1) # white mean =47.06, median=45

worry2<-Baseline%>%
  filter(race_bl=="Black or African American")

summary(worry2$worry_bl_1) # black mean =52.6, median =50.5

# average worry in blacks and whites by week
AvWorryWhites <-MSV4models %>%
  group_by(surveydate, race_bl) %>%
  summarise(mean=mean(CovidGet_1,na.rm=TRUE)) %>%
  group_by(race_bl) %>%
  summarise(grandmean=mean(mean), sd=sd(mean)) 

# plot distribution of worry score for each race by week
p<-MSV4models %>%
  filter(race_bl %in% c("White", "Black or African American")) %>%
  group_by(surveydate, race_bl) %>%
  summarise(mean=mean(CovidGet_1,na.rm=TRUE)) %>%
  ggplot(aes(surveydate, mean, color=race_bl)) +
  geom_point() +
  geom_line() +
  ylim(0,100)

p

```



# Make figure plus table
```{r}
# See https://cran.r-project.org/web/packages/forestplot/vignettes/forestplot.html
# Cochrane data from the 'rmeta'-package
table <- structure(list(mean  = c(NA, NA, 1.20, 2.26, 5.02), 
                                      lower = c(NA, NA, 0.9, 1.75, 3.88),
                                      upper = c(NA, NA, 1.60, 2.91, 6.49)),
                                 .Names = c("mean", "lower", "upper"), 
                                 row.names = c(NA, -5L), 
                                 class = "data.frame")

tabletext <- cbind(c("", "Case count category", "1157.27 to <2265.5 vs. <1157.25", "2265.5 to <3331 vs. <1157.25", "≥3331 vs. <1157.25"),
                   c("OR (95% CI)", " ", "1.20 (0.9 to 1.60)", "2.26 (1.75 to 2.91)", "5.02 (3.88 to 6.49)"))
                   
pdf("Figure2.pdf")
table %>% 
  forestplot(labeltext = tabletext, 
             boxsize=0.1,
             is.summary = c(TRUE, TRUE, FALSE, FALSE, FALSE),
             #clip = c(0.1, 2.5), 
             xlog = TRUE, 
             col = fpColors(box = "royalblue",
                            line = "darkblue",
                            summary = "royalblue"),
             xlab="OR")
dev.off()
```



