---
title: "Protective Behaviors Paper"
author: "Kim Johnson"
date: '2022-07-01'
output: html_document
---
# Load packages and libraries 
```{r}
pacman::p_load(readxl, openxlsx, table1, dplyr, ggplot2, Hmisc, vtable, tidyr, ggrepel, segmented, lubridate, miceadds, lme4, readr, lubridate, lmtest, multcomp, patchwork)
```

# Import files used for the analysis
```{r}
# import most recent survey file for iheard
Merged_survey <- read.xlsx("SurveyExport_Merged.xlsx")

# set date format
Merged_survey$surveydate<-as.Date(Merged_survey$surveydate,origin="1899-12-30", format = "%Y-%m-%d")

# Filtering for survey dates between 10/17/2021 and 7/1/2022 that are included in the study
Merged_survey <- Merged_survey %>%
  filter(surveydate < "2022-07-01" & surveydate >= "2021-10-17") %>%
  dplyr::select(ExternalReference, surveydate, PreventionFreq, COVIDStatus, CovidGet_1, COVIDSerious_1,gender_bl, age_cat, race_bl)

# read in Baseline data for Table 1
Baseline<-read_excel("Baseline.xlsx") # for Table 1

# limit Baseline ids to those in merged survey (dates 10/17/2021 to 7/1/2022)
ids<-unique(Merged_survey$ExternalReference)

# filter for ids in merged survey
Baseline<-Baseline %>%
  filter(ExternalReference %in% ids)
```

# Import STL City and County COVID-19 cases and hospitalizations (from the MO Hospital Organization)
```{r}
# cases and hospitalizations, first set sent 
COVID_MOcases1<-read_delim("MO Hospital association files/County Data.csv")

COVID_MOhosp1<-read_delim("MO Hospital association files/Teletracking.csv")

# cases and hospitalizations, first set sent 
COVID_MOcases2<-read_delim("MO Hospital association files/County(through June 22).csv")

COVID_MOhosp2<-read_delim("MO Hospital association files/Hospital(through June 22).csv")
```

# Data management for case counts used in analysis
```{r}
# Limit case counts to St. Louis City and County
COVID_STcases1<-COVID_MOcases1 %>%
  filter(County_Desc %in% c("SAINT LOUIS", "SAINT LOUIS CITY")) %>%
  group_by(week_begining) %>%
  summarise(sum=sum(pcr_cases)) # sums Saint Louis and Saint Louis City

COVID_STcases2<-COVID_MOcases2 %>%
  filter(County_Desc %in% c("SAINT LOUIS", "SAINT LOUIS CITY")) %>%
  filter(week_begining %in% c("5/29/2022", "6/5/2022", "6/12/2022", "6/19/2022", "6/26/2022")) %>%
  group_by(week_begining) %>%
  summarise(sum=sum(pcr_cases)) # sums Saint Louis and Saint Louis City

# Bind case counts together
COVID_STcases<-rbind(COVID_STcases1, COVID_STcases2)

# Limit hospitalizations to St. Louis Region
COVID_SThosp1<-COVID_MOhosp1%>%
  filter(region=="Saint Louis Region") %>%
  rename(week_begining=dt)

COVID_SThosp2<-COVID_MOhosp2%>%
  filter(region=="Saint Louis Region")%>%
  filter(dt %in% c("5/29/2022", "6/5/2022", "6/12/2022", "6/19/2022", "6/26/2022")) %>%
  rename(week_begining=dt) 

# Bind hospitalization counts together
COVID_SThosp<-rbind(COVID_SThosp1, COVID_SThosp2)
```

# Get participants by week (first paragraph of results)
```{r}
partbywk<-Merged_survey %>%
  group_by(surveydate) %>%
  summarise(n=n())

summary(partbywk$n)
```

# Get number of surveys by participant (first paragraph of results)
```{r}
survbypart<-Merged_survey %>%
  filter(surveydate < "2022-07-01" & surveydate >= "2021-10-17") %>%
  group_by(ExternalReference) %>%
  summarise(n=n())

summary(survbypart$n)
```

# Table 1：Descriptive analysis of demographics
```{r}
# Some data management to get correct order of variables
Baseline$age_cat<-factor(Baseline$age_cat, levels = c("18-29", "30-39", "40-49", "50-59", "≥60"))
Baseline$gender_bl<-factor(Baseline$gender_bl, levels = c("Male", "Female", "Non-binary / third gender", "Prefer not to say"))
Baseline$hispanic_bl<-factor(Baseline$hispanic_bl, levels = c("Yes", "No", "Prefer not to say"))

Baseline$race_bl<-
  ifelse(Baseline$race_bl == "White", Baseline$race_bl,
    ifelse(Baseline$race_bl == "Black or African American", Baseline$race_bl,
      ifelse(Baseline$race_bl == "Asian or Asian American", Baseline$race_bl,
        ifelse(Baseline$race_bl == "Prefer not to say", Baseline$race_bl,
          ifelse(Baseline$race_bl == "Other (please specify)", "Other", "Two or more races")))))
Baseline$race_bl<-factor(Baseline$race_bl, levels = c("White", "Black or African American", "Asian or Asian American", "Two or more races", "Other", "Prefer not to say"))

Baseline$under12_bl<-factor(Baseline$under12_bl, levels = c("Yes", "No"))
Baseline$vax_received_bl<-factor(Baseline$vax_received_bl, levels = c("Yes, both doses of a 2-dose vaccine", "Yes, first dose of a 2-dose vaccine", "Yes, a 1-dose vaccine", "No, but I plan to get a COVID-19 vaccine", "No, and I don't plan to get a COVID-19 vaccine", "Prefer not to answer"))

# apply labels for table 1
label(Baseline$gender_bl)<-"Gender"
label(Baseline$race_bl)<-"Race"
label(Baseline$hispanic_bl)<-"Hispanic Ethnicity"
label(Baseline$partype)<-"Participant Type"
label(Baseline$vax_received_bl)<-"Vaccination Status"
label(Baseline$age_cat)<-"Age Category (years)"

# Table 1
table1(~gender_bl  + race_bl + hispanic_bl + age_cat + vax_received_bl, Baseline)
```

# Create file to get percentages of protective behaviors and factor PreventionFreq
```{r}
# get percentages of protection behaviors f
PF<-Merged_survey %>%
  group_by(surveydate, PreventionFreq) %>%
  filter(!is.na(PreventionFreq)) %>%
  summarise(Percentage=n()) %>% 
  mutate(Percentage=Percentage/sum(Percentage)*100) 

PF$PreventionFreq <- factor(PF$PreventionFreq, levels=c("About the same as you did one week ago?", "Less than you did one week ago?", "More than you did one week ago?"), labels=c("Same", "Less", "More Prevention Behaviors"))
```

# Data management for plotting covid status (self or close contact infected)
```{r}
# get all items indicating infection in self or close contact
CovidStat<-Merged_survey %>%
  mutate(CS_infection=if_else(grepl('household_closecontact',COVIDStatus)|
                               grepl('household_test', COVIDStatus)|
                               grepl('household_sick', COVIDStatus)|
                               grepl('household_hospital', COVIDStatus), 1, 0)) %>%
  mutate(CS_none=if_else(grepl('household_none', COVIDStatus), 1, 0))

CovidStat$CS_infection <- factor(CovidStat$CS_infection, levels=c(1:0), labels=c("Self or close contact COVID infected", "No one COVID infected"))

table(CovidStat$CS_infection)
table(CovidStat$CS_none)
```

# Create file to get percentages of self or close contact having covid infection in last week
```{r}
# CS_infected
CovidStat2<-CovidStat %>%
  group_by(surveydate, CS_infection) %>%
  summarise(Percentage=n()) %>% 
  mutate(Percentage=Percentage/sum(Percentage)*100) 
```

# Create dataframe limiting to % more protective behaviors
```{r}
PF_limited<-PF %>%
  filter(PreventionFreq=="More Prevention Behaviors") 
PF_limited<-as.data.frame(PF_limited)
```

# Create dataframe limiting to % infection in self or clost contact 
```{r}
CovidStat3_limited<-CovidStat2 %>%
  filter(CS_infection=="Self or close contact COVID infected") 

CovidStat3_limited<-as.data.frame(CovidStat3_limited)

new_row5 <- data.frame("2021-10-10", "Self or close contact COVID infected", 0)
names(new_row5)<-c("surveydate","CS_infection","Percentage")
new_row6 <- data.frame("2022-02-27", "Self or close contact COVID infected", 0)
names(new_row6)<-c("surveydate","CS_infection","Percentage")
CovidStat3_limited <- rbind(CovidStat3_limited, new_row5, new_row6) %>% 
  arrange(surveydate)
```

# Match survey date with MO HOSP files week beginning dates 
```{r}
# function to align survey dates to use for merging
fixdates<-function(data){
data<-data %>%
  mutate(week_begining=case_when(surveydate== "2021-08-30" ~"8/29/2021",
                                  surveydate=="2021-09-06" ~"9/5/2021",
                                  surveydate=="2021-09-07" ~"9/5/2021",
                                  surveydate=="2021-09-13" ~"9/12/2021",
                                  surveydate=="2021-09-15" ~"9/12/2021",
                                  surveydate=="2021-09-20" ~"9/19/2021",
                                  surveydate=="2021-09-21" ~"9/19/2021",
                                  surveydate=="2021-09-26" ~"9/26/2021",
                                  surveydate=="2021-10-03" ~"10/3/2021",
                                  surveydate=="2021-10-10" ~"10/10/2021",
                                  surveydate=="2021-10-17" ~"10/17/2021",
                                  surveydate=="2021-10-24" ~"10/24/2021",
                                  surveydate=="2021-10-31" ~"10/31/2021",
                                  surveydate=="2021-11-07" ~"11/7/2021",
                                  surveydate=="2021-11-14" ~"11/14/2021",
                                  surveydate=="2021-11-21" ~"11/21/2021",
                                  surveydate=="2021-11-28" ~"11/28/2021",
                                  surveydate=="2021-12-05" ~"12/5/2021",
                                  surveydate=="2021-12-12" ~"12/12/2021",
                                  surveydate=="2021-12-19" ~"12/19/2021",
                                  surveydate=="2021-12-26" ~"12/26/2021",
                                  surveydate=="2022-01-02" ~"1/2/2022",
                                  surveydate=="2022-01-09" ~"1/9/2022",
                                  surveydate=="2022-01-16" ~"1/16/2022",
                                  surveydate=="2022-01-23" ~"1/23/2022",
                                  surveydate=="2022-01-30" ~"1/30/2022",
                                  surveydate=="2022-02-06" ~"2/6/2022",
                                  surveydate=="2022-02-13" ~"2/13/2022",
                                  surveydate=="2022-02-20" ~"2/20/2022",
                                  surveydate=="2022-02-27" ~"2/27/2022",
                                  surveydate=="2022-03-06" ~"3/6/2022",
                                  surveydate=="2022-03-13" ~"3/13/2022",
                                  surveydate=="2022-03-20" ~"3/20/2022",
                                  surveydate=="2022-03-27" ~"3/27/2022",
                                  surveydate=="2022-04-03" ~"4/3/2022",
                                  surveydate=="2022-04-10" ~"4/10/2022",
                                  surveydate=="2022-04-17" ~"4/17/2022",
                                  surveydate=="2022-04-24" ~"4/24/2022",
                                  surveydate=="2022-05-01" ~"5/1/2022",
                                  surveydate=="2022-05-08" ~"5/8/2022",
                                  surveydate=="2022-05-15" ~"5/15/2022",
                                  surveydate=="2022-05-22" ~"5/22/2022",
                                  surveydate=="2022-05-29" ~"5/29/2022",
                                  surveydate=="2022-06-07" ~"6/5/2022",
                                  surveydate=="2022-06-13" ~"6/12/2022",
                                  surveydate=="2022-06-19" ~"6/19/2022",
                                  surveydate=="2022-06-26" ~"6/26/2022"
                                  ))
}

PF_limited<-fixdates(PF_limited) # adds week_begining to PF_limited file

CovidStat<-fixdates(CovidStat) # adds week_begining to CovidStat file

CovidStat3_limited<-fixdates(CovidStat3_limited) # adds week_begining to CovidStat3_limited file

# merge PF_limited with COVID_STcases to get St. Louis City and County cases in one dataset for graphing (through June 2022)
PF_limited<-left_join(PF_limited, COVID_STcases, by="week_begining")

# merge CovidStat with COVID_STcases that goes through June 2022
CovidStat<-left_join(CovidStat, COVID_STcases, by="week_begining")

# merge CovidStat3_limited (close contact infection) with COVID_STcases that goes through June 2022
CovidStat3_limited<-left_join(CovidStat3_limited, COVID_STcases,  by="week_begining")
```

# Prepare analytic dataset
```{r}
# create analytic dataset
MSV4models<-CovidStat %>%
  dplyr::select(ExternalReference, PreventionFreq, CS_infection, CS_none, surveydate, sum, gender_bl, age_cat, week_begining, race_bl, CovidGet_1)
```

# Data management for graphs for More Protective Behaviors in association with case counts, positive household contacts
```{r}
# delete dates without case counts and create datasets to merge into one big dataset
PF_limited1<-PF_limited %>%
  filter(!is.na(sum)) %>%
  rename(STL_Cases=sum, Variable=PreventionFreq) # more protective behaviors than last week

CovidStat3_limited1<-CovidStat3_limited %>%
  filter(!is.na(sum)) %>%
  rename(STL_Cases=sum, Variable=CS_infection)  # infection last week

# rbind together
Data4Plot<-rbind(PF_limited1, CovidStat3_limited1)

# covert to date formats
Data4Plot$week_begining<-as.Date(Data4Plot$week_begining, "%m/%d/%Y")


# drop dates 10/17/2022 or earlier due to small numbers
Data4Plot<-Data4Plot %>%
  filter(surveydate>="2021-10-17")
```


# Figure 1 
```{r}
p1<-Data4Plot %>%
  group_by(surveydate) %>%
  filter(Variable %in% c("More Prevention Behaviors", "Self or close contact COVID infected")) %>%
  
ggplot() + 
  geom_line(size = 1, aes(surveydate, Percentage, color=Variable)) +
  geom_line(size = 1, aes(week_begining, STL_Cases/200, color = "St. Louis Region PCR positive cases"), inherit.aes = FALSE) +
  scale_color_manual(NULL, values = c("blue","black","tomato3"), 
                                      labels = c('More protective behaviors','Self or close contact COVID-19 infected','St. Louis Region PCR positive COVID-19 cases'))+
        ylim(0,100)  +
  # geom_point(aes(week_begining, STL_Cases/200, color = "St. Louis Region PCR positive cases"), inherit.aes = FALSE) +
  scale_y_continuous(sec.axis=sec_axis(~.*200, name="St. Louis Region PCR positive cases")) +
  xlab("Date") + 
  scale_x_date(date_labels="%m-%d-%y", breaks=Data4Plot$surveydate, date_breaks="2 weeks")+
  theme(axis.text.y.right=element_text(colour="tomato3", size = 12),
        axis.title.y.right=element_text(colour="black", vjust = 1.5, size = 16, face = "bold"),
        axis.text.y=element_text(colour="black", size = 12, face="bold"),
        axis.title.y=element_text(colour="black", vjust = 3, size = 16, face = "bold"),
        axis.title.x=element_blank(),
        legend.position="bottom",
        legend.title = element_blank(),
        legend.key = element_blank(),
        legend.text = element_text(face = "bold", size = 16),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.background = element_blank(),
        axis.line = element_line(colour = "black"),
        axis.text.x = element_text(colour = "black", angle = 90, hjust = 1, size = 12, face = "bold")) +
        guides(colour = guide_legend(nrow = 3))
p1 


pdf("Figure1.pdf", width=15, height=10, paper="USr")
p1  + plot_layout(ncol=1, nrow=1, guides='keep') &
  theme(legend.position='bottom')
dev.off()
```


# Dataset for logistic analyses that asks whether individuals report more protective behaviors than the week before when case counts are high or when they are sick or a close contact is sick
```{r}
# creating the binary MoreProtect dependent and CloseContact independent variables
MSV4models <- MSV4models %>%
  mutate(MoreProtect = if_else(PreventionFreq == 'More than you did one week ago?', 1 , 0)) %>%
  mutate(CloseContact= if_else(CS_infection=="Self or close contact COVID infected", 1, 0)) 

# get quartiles based on survey days, need to limit dataset to unique dates to get accurate quartiles
dates<-MSV4models %>%
  dplyr::select(surveydate, sum)
dates<-unique(dates)

# get quantiles
quantile(dates$sum, na.rm = TRUE) 

MSV4models <- MSV4models%>% # make quartile categories for case counts
  mutate(CC_cat = if_else(sum< 1051, 0 ,
                          if_else(sum >=1051 & sum<2147, 1,
                                 if_else(sum >=2147 & sum<3306, 2,
                                        if_else(sum>=3306, 3, NULL)))))
MSV4models$CC_cat<-as.factor(MSV4models$CC_cat)
table(MSV4models$CC_cat)

# plot MoreProtect by survey data according to CC_cat for each participant to look at patterns
p<-ggplot(MSV4models) +
  geom_point(aes(surveydate, MoreProtect,  color=CC_cat)) +
  facet_wrap(~ExternalReference)
p
```


# Table 2: Mixed logistic models for case count category
```{r}
# create a rank variable for dates
unique <- as.data.frame(unique(MSV4models$surveydate))
unique <- rename(unique, "surveydate" = c("unique(MSV4models$surveydate)"))
unique$rank <-rank(unique$surveydate)

# merge rank into MSV4models
MSV4models <- left_join(MSV4models, unique, by = "surveydate")

# Is case count category associated with more protective behavior than the week before? # rank/ExternalReference can be interpreted as surveydate within each subject. This gives us a random intercept and slope for each subject
glmer_glmCC <- glmer(data = MSV4models, MoreProtect ~ CC_cat + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC)

cc2<-exp(confint.merMod(glmer_glmCC, method="Wald"))[-c(1:4),]
est <- as.data.frame(exp(fixef(glmer_glmCC)))[-c(1),]
ctab2<-as.data.frame(cbind(est, cc2))
colnames(ctab2)

# results table for cc_cat
ctab2<-rename(ctab2,"OR" = c("est"),
                    "low CI" = c("2.5 %"),
                    "high CI" = c("97.5 %"))

print(ctab2)
```

#  Table 2: CloseContact adjusted for case count
```{r} 
glmer_glm5<- glmer(data= MSV4models, MoreProtect ~  CC_cat + CloseContact + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glm5)

cc5<-exp(confint.merMod(glmer_glm5, method="Wald"))[-c(1:4),]
est <- as.data.frame(exp(fixef(glmer_glm5)))[-c(1),]
ctab5<-as.data.frame(cbind(est, cc5))
colnames(ctab5)

ctab5 <-rename(ctab5,"OR" = c("est"),
                    "low CI" = c("2.5 %"),
                    "high CI" = c("97.5 %"))
print(ctab5)
```
# Effect modification (analyses only limited to males and females) (paragraph 4 results)
```{r}
# limit to males and females
MSV4models_gen<-MSV4models %>%
  filter(gender_bl %in% c("Female", "Male"))

# run gender model without interaction term
glmer_glmCC_genb<- glmer(data= MSV4models_gen, MoreProtect ~ CC_cat  + gender_bl + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_genb)

# run gender model with interaction term
glmer_glmCC_gen<- glmer(data= MSV4models_gen, MoreProtect ~ CC_cat  +  gender_bl + gender_bl*CC_cat +  rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_gen)

# get significance of interaction term
lrtest(glmer_glmCC_gen, glmer_glmCC_genb)

# Gender is not significant
```

# Effect modification (age)  (paragraph 4 results)
```{r}
# collapse age categories
MSV4models_age <- MSV4models %>%
  mutate(age_cat2=case_when(age_cat %in% c("18-29", "30-39")~0,
         age_cat %in% c("40-49", "50-59") ~1,
         age_cat %in% c(">60") ~2)) # note this is mislabelled in survey_merged. It should be ≥60

table(MSV4models_age$age_cat2)

# case count category
glmer_glmCC_age<- glmer(data= MSV4models_age, MoreProtect ~ CC_cat + as.factor(age_cat2) + as.factor(age_cat2)*CC_cat + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_age)

# run age model
glmer_glmCC_ageb<- glmer(data= MSV4models_age, MoreProtect ~ CC_cat + as.factor(age_cat2)  + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_ageb)

# get global significance of interaction term
lrtest(glmer_glmCC_age, glmer_glmCC_ageb)
```

# Effect modification (analyses only limited to Whites and Black or African American) (paragraph 4 results)
```{r}
MSV4models_race<-MSV4models %>%
  filter(race_bl %in% c("White", "Black or African American")) %>%
  mutate(race_bl2=case_when(race_bl==c("White") ~0,
                            race_bl==c("Black or African American")~1)) # reverse reference

# run model without interaction term
glmer_glmCC_raceb<- glmer(data= MSV4models_race, MoreProtect ~ CC_cat+ race_bl + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_raceb)

# run model with interaction term
glmer_glmCC_race<- glmer(data= MSV4models_race, MoreProtect ~ CC_cat + race_bl + race_bl*CC_cat + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_race)

# get significance of interaction term
lrtest(glmer_glmCC_race, glmer_glmCC_raceb)

# Interaction is significant
```
# Table 2: Stratified estimates by race (case count category) 
```{r}
# Whites
MSV4models_white<-MSV4models %>%
  filter(race_bl %in% c("White"))

glmer_glmCC_white<- glmer(data= MSV4models_white, MoreProtect ~ CC_cat  + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_white)

cc7<-exp(confint.merMod(glmer_glmCC_white, method="Wald"))[-c(1:4),]
est <- as.data.frame(exp(fixef(glmer_glmCC_white)))[-c(1),]
ctab7<-as.data.frame(cbind(est, cc7))
colnames(ctab7)

ctab7a <-rename(ctab7,"OR" = c("est"),
                    "low CI" = c("2.5 %"),
                    "high CI" = c("97.5 %"))
print(ctab7a)

# Black or African American
MSV4models_black<-MSV4models %>%
  filter(race_bl %in% c("Black or African American"))

glmer_glmCC_black<- glmer(data= MSV4models_black, MoreProtect ~ CC_cat   +rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_black)

cc8<-exp(confint.merMod(glmer_glmCC_black, method="Wald"))[-c(1:4),]
est <- as.data.frame(exp(fixef(glmer_glmCC_black)))[-c(1),]
ctab8<-as.data.frame(cbind(est, cc8))
colnames(ctab8)

ctab8a <-rename(ctab8,"OR" = c("est"),
                    "low CI" = c("2.5 %"),
                    "high CI" = c("97.5 %"))
print(ctab8a)
```

# Close contact interactions gender (paragraph 5 results)
```{r}
# gender
glmer_glmCC_gen1<- glmer(data= MSV4models_gen, MoreProtect ~ CC_cat + CloseContact + gender_bl  + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_gen1)

glmer_glmCC_gen<- glmer(data= MSV4models_gen, MoreProtect ~ CC_cat + CloseContact + gender_bl + gender_bl*CloseContact + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_gen)

lrtest(glmer_glmCC_gen1, glmer_glmCC_gen)
```

# Close contact interactions age (paragraph 5 results)
```{r}
glmer_glmCC_age1<- glmer(data= MSV4models_age, MoreProtect ~ CC_cat + CloseContact + as.factor(age_cat2)  + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_age1)

glmer_glmCC_age<- glmer(data= MSV4models_age, MoreProtect ~ CC_cat +CloseContact + as.factor(age_cat2) + as.factor(age_cat2)*CloseContact + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_age)

lrtest(glmer_glmCC_age1, glmer_glmCC_age)
```

# Close contact interactions race (paragraph 5 results)
```{r}
glmer_glmCC_race1<- glmer(data= MSV4models_race, MoreProtect ~ CC_cat + CloseContact + race_bl2  + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_race1)

glmer_glmCC_race2<- glmer(data= MSV4models_race, MoreProtect ~  CC_cat + CloseContact + race_bl2 + race_bl2*CloseContact + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_race2)

# get significance of interaction term
lrtest(glmer_glmCC_race1, glmer_glmCC_race2)
```

# Table 2: Stratified estimates by race (close contact)
```{r}
# Whites
MSV4models_white<-MSV4models %>%
  filter(race_bl %in% c("White"))

table1(~CC_cat|MoreProtect, MSV4models_white)

glmer_glmCC_white<- glmer(data= MSV4models_white, MoreProtect ~ CC_cat + CloseContact  + rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_white)

cc7<-exp(confint.merMod(glmer_glmCC_white, method="Wald"))[-c(1:4),]
est <- as.data.frame(exp(fixef(glmer_glmCC_white)))[-c(1),]
ctab7<-as.data.frame(cbind(est, cc7))
colnames(ctab7)

ctab7 <-rename(ctab7,"OR" = c("est"),
                    "low CI" = c("2.5 %"),
                    "high CI" = c("97.5 %"))
print(ctab7)

# Black or African American
MSV4models_black<-MSV4models %>%
  filter(race_bl %in% c("Black or African American"))

glmer_glmCC_black<- glmer(data= MSV4models_black, MoreProtect ~ CC_cat  + CloseContact +rank + (rank|ExternalReference), family = binomial, control=glmerControl(optimizer="bobyqa",optCtrl=list(maxfun=2e5)))
summary(glmer_glmCC_black)

cc8<-exp(confint.merMod(glmer_glmCC_black, method="Wald"))[-c(1:4),]
est <- as.data.frame(exp(fixef(glmer_glmCC_black)))[-c(1),]
ctab8<-as.data.frame(cbind(est, cc8))
colnames(ctab8)

ctab8 <-rename(ctab8,"OR" = c("est"),
                    "low CI" = c("2.5 %"),
                    "high CI" = c("97.5 %"))
print(ctab8)
```


# For revision (table showing how many people completed each week's survey)
```{r}
# of surveys completed by date
survyno <- MSV4models %>%
  group_by(surveydate) %>%
  tally()

# of surveys completed by individual

survyno_ind <- MSV4models %>%
  group_by(ExternalReference) %>%
  tally()

summary(survyno_ind$n)

sheets<-list("Surveys completed by date" = survyno)
write.xlsx(sheets, file="Supplementary_tables.xlsx", keepNA=TRUE, overwrite=TRUE)
```


